Analyzing the impact of social attributes on commit integration success

### 2017-02-20 Paper/MSRChallenge2017.tex
minor revisions to the beginning of the paper

\textbf{Comparing two data sets:} We used the social data gathered to create two data 
sets: one with only the technical
factors and the build status, and another with both the technical and social
factors, this is to be able to compare how well can the job status be predicted 
by just technical data, and adding social data.

@@

Since we are interested in the success of the job status of each row, we 
converted the Travis build statuses to just two possible values,
successful (passed in the original provided data set) and not successful 
(errored, failed, canceled
and started in the original data set). At this point we had a 3:1 successful to 
not successful ratio in the rows of the data sets.

@@

To avoid this and have a 1:1 ratio successful to not successful, we created a 
separate data set where the
successful builds were a random sub-sample of successful builds were selected
such that the number of successful builds equaled the number of failing builds,
known as downsampling.  We used 
both the downsampled and non-downsampled data sets in our results to show the 
difference of the behavior of the decision tree when it is trained with a equal 
ratio than when it is trained with a non equal ratio.

>>>>

\textbf{Comparing two data sets:} We used the social data gathered to create two data 
sets: one with only the technical
factors and the build status, and another with both the technical and social
factors. We performed this split to analyze how well job status be predicted 
by just technical factors, and then with additional social factors.

@@

Since we are interested in the success of the job status of each row, we 
converted the Travis build statuses to just two possible values,
successful (passed in the original provided data set) and not successful 
(errored, failed, canceled
and started in the original data set). We also condensed down all passing and
failing builds in a commit to a single pass or fail for each build status.
At this point we had a 3:1 successful to 
not successful ratio in the rows of the data sets.

@@

The high ratio of successful to not successful builds cause the classifier to 
favor misclassifying not successful builds over successful builds, because a 1\%
misclassification rate in 3/4th of the data is greater than a 1\%
misclassification rate in 1/4th of the data.  To penalize misclassification for
both classes equally, we created a separate data set where the
successful builds equaled the number of not successful builds.  
We build this data set by copying over all not successful builds and randomly
selecting a sub-sample of the successful builds until the two build status were
equal, known as downsampling.  We used 
both the downsampled and non-downsampled data sets in our results to show the 
difference of the behavior of the decision tree when it is trained with a equal 
ratio than when it is trained with a unequal ratio.
